Supplementary Materials

### 2018-03-30 paper/application.tex
minor fix

As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair, the word \textbf{pile} and \textbf{heap} is not well-aligned (see Fig.~\ref{fig:att2pred}(a)).
%
To test whether the alignment is what contribute to the misclassification, the domain expert utilizes the attention editing functionality in the matrix attention view (Fig.~\ref{fig:attentionVis}(c)) to make the word \textbf{pile} align with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
%
As illustrated in Fig.~\ref{fig:att2pred} (d), after the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary (Fig.~\ref{fig:att2pred}(d)), but the corrected attention fails to produce a conclusive \emph{entailment} prediction.
%
%Interestingly, the original pair's attention is almost identical to the edited attention (the comparison is not shown in the figure). 
Such an observation implies that the model does not firmly believe ``\textbf{heap} of snow'' and ``\textbf{pile} of snow'' have the same meaning, which may indicate the potential issue with the encoder or word embedding.

@@

%\shusen{Example where the prediction is correct but the alignment is wrong}
%%%% are we obtain correct prediction from wrong alignment %%%%%
%By looking into the model decision making process, we can assess whether the model is behaving as intended. For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
We have shown that the perfect alignment does not necessarily guarantee a correct prediction.
%
On the flip side, we may produce the right predictions for the ``wrong'' reason (i.e., incorrect attention). 
%As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, 
For example the sentence pair (\emph{H}: ``A couple is taking a break from bicycling.'', \textbf{H}: ``sisters sit next to their bikes.''). The word \textbf{take} and \textbf{next} should not align with each other,
%(Fig.~\ref{fig:wrongAlignRightPred}(a)), 
yet, it still produce the correct \emph{neutral} label.% (Fig.~\ref{fig:wrongAlignRightPred}(b)).
%
%By looking into the model decision making process, we can assess whether the model is behaving as intended. 
%These situations demonstrate the important of understanding the model decision making process, we can assess whether the model is behaving as intended.

>>>>

As illustrated in Fig.~\ref{fig:att2pred}(a), based on the graph attention visualization, we can see in the attention for (\textbf{P}, \textbf{H2}) pair, the word \textbf{pile} and \textbf{heap} is not well-aligned (see Fig.~\ref{fig:att2pred}(a)).
%
To test whether the alignment is what contribute to the misclassification, the domain expert utilizes the attention editing functionality in the matrix attention view (Fig.~\ref{fig:attentionVis}(c)) to make the word \textbf{pile} align with \textbf{heap} (shown in Fig.~\ref{fig:att2pred}(b)).
%
As illustrated in Fig.~\ref{fig:att2pred} (d), after the edit, the original prediction (Fig.~\ref{fig:att2pred}(c)) has been moved from neutral to the classification boundary (Fig.~\ref{fig:att2pred}(d)), but the corrected attention fails to produce a conclusive \emph{entailment} prediction (a case where the attention edit corrects the final prediction is shown in Fig.~ref{fig:depTreeExample}).
%
%Interestingly, the original pair's attention is almost identical to the edited attention (the comparison is not shown in the figure). 
Such an observation implies that the model does not firmly believe ``\textbf{heap} of snow'' and ``\textbf{pile} of snow'' have the same meaning, which may indicate the potential issue with the encoder or word embedding.

@@

%\shusen{Example where the prediction is correct but the alignment is wrong}
%%%% are we obtain correct prediction from wrong alignment %%%%%
%By looking into the model decision making process, we can assess whether the model is behaving as intended. For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
We have shown that the perfect alignment does not necessarily guarantee a correct prediction.
%
On the flip side, we may produce the right predictions for the ``wrong'' reason (i.e., incorrect attention). 
%As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, 
For example, in the sentence pair (\textbf{P}: ``A couple is taking a break from bicycling.'', \textbf{H}: ``sisters sit next to their bikes.''), the word \textbf{take} and \textbf{next} should not align with each other,
%(Fig.~\ref{fig:wrongAlignRightPred}(a)), 
yet, it still produce the correct \emph{neutral} label.% (Fig.~\ref{fig:wrongAlignRightPred}(b)).

%By looking into the model decision making process, we can assess whether the model is behaving as intended. 
%These situations demonstrate the important of understanding the model decision making process, we can assess whether the model is behaving as intended.
